### 2024-09-10 texts/paper_closing.tex
move conclusion paragraphs around, tryiing to find good angle

% Created 2024-09-09 ma 10:48
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

Due to the founders central role, private museums have been argued to be highly dependent on their founder for their continuing existence, as museums generally cannot cover expenses via revenues from ticket prices, museum shops and cafes:
The \textcite{IMLS_2008_funding} found that for non-profit American art museums, less than half (48.1\%) the revenues come from earned income, leaving substantial gaps in the budgets that are filled by a mix of private donations (23.0\%), investment (18.5\%) and government support (10.4\%) (p.27).
Outside of the United States, the reliance on revenue streams beyond operations is even larger:
German museums in the 1990s covered on average only 27\% of their expenses covered by operations \parencite[p.233]{Martin_1993_museen}, and even the more market-oriented NPOs in the cultural sector draws around 50\% of their funding from public support \parencite[p.82]{Zimmer_Priller_2007_gemeinnuetzig}.

@@

On a national level, density of private museum is calculated as the number of private museums per million.
On a local level, I use the Global Human Settlement Layer \parencite{EC_2023_GHSL} to estimate the number of private museums and population counts inside a radius of ten kilometers around each private museum for each year.
To be able to estimate both competition and demand/audience/population separately, I do not calculate densities as per capita rates, but include the local museum counts, local population in millions as well as an interaction between the two.
\subsubsection*{Control variables}

@@

Investigating the survival prospects of private museum furthermore illucidates the long-term development of the organizational form as a whole, as it provides insights into factors related to variation of sustainability and thereby into trends in composition.

The lack of a relation between temporary exhibitions and survival prospect is somewhat unexpected.
It was expected that as temporary exhibitions constitute one of the main tasks of a museums operations, organizing them would benefit a museum financially (via visitor fees) and symbolically (via prestige of other art field actors, which might be developed into further contacts), leading to higher survival chances\footnote{Furthermore, the ability to organization exhibitions likely reflects museum resources, which should also enhance survival.}
However, organizing exhibitions does not seem to bestow benefits for the museums which organize them, nor do organizations seem to be organized only by established/sustainable/secure organizations.
One possibility for this discrepancy could be that exhibitions are expensive, and whatever benefits gained from them are offset by the associated costs.
One might see in this association again the importance of the founder:
Founders who are committed to their museums will keep them alive, regardless of whether or not they plan to organize temporary exhibitions.
\subsubsection*{founder}

It has been widely argued that the death of the founder would lead to his or her private museum to close, while this analysis has not found conclusive evidence for this relationship.
It is important to keep in mind that the lack of observing a clear relationship between the death of the founder and museum closure does not imply that no relationship exists.
It is possible that previous scholars who argued for such an association have correctly identified the dependency relationships in private museums, which will become visible once more founder deaths have occurred.
At the same time, it is possible that private museums are indeed generally less dependent on the mood of a single person (or couple), and have in fact become institutionalized to an extent that heirs of founders feel as motivated to continue the original founders' efforts as these founders themselves.
\subsection*{Conclusion}

Private museum have been characterized as fragile institutions due to their reliance on a single founder.
However, my analysis finds neither a higher substantially higher mortality rates for private museums compared to (art) museums generally, nor a conclusive relationship between museum closure and a number of founder characteristics, such as founder gender, death, exclusion from the Artnews collector ranking or inclusion of founder name in the museum name.
While Self-identification and audience/competition are significantly associated with higher mortality, and possibly reflect or influence founder motivations, they are also subject to alternative mechanisms, namely devaluation by third parties and competition, respectively (self-identification furthermore concerns a relatively small group of institutions).
Furthermore, even if they reflect founder motivations, these are likely cases of voluntary closure; there is thus no large evidence that private museums are at a higher risk of unvoluntary closure than more diversified museums as a consequence of their reliance on a single founder.

A possible explanation of the characterization of private museums as fragile might be due to the focus on case studies, which disregards the much larger population who don't experience closing.
Due to the "private museum boom", some museums will experience closing over a period of around two decades even if the underlying closing probability is low.

It cannot be stated whether private museums experience higher mortality rates than publicly funded museums (for which European countries would be the most natural comparison).
While public museums have been characterized to some extent as very stable due to government picking up deficits \parencite{Meier_Frey_2003_faces,Bechtler_Imhof_2018_future}, \textcite{Walker_2019_collector} argues that due to declining cultural spending even public museums might face hard times.
While national public flagship institutions will likely remain sufficiently funded to survive, this might not be the case for the vast majority of smaller museums in less touristic regions who rely on limited municipal funding, as \textcite{StylianouLambert_etal_2014_museums} demonstrate for a number of smaller publicly funded ethnography museums in Cyprus.
Without access to museum register comparable to the IRS/NCCS datasets, such questions regarding the relation between type of ownership and survival remain speculative.

\begin{sloppypar}
\printbibliography
\end{sloppypar}
\subsubsection*{Limitations}

@@

egmus doesn't have that
\end{document}

>>>>

% Created 2024-09-10 di 19:08
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

Due to the founders central role, private museums have been argued to be highly dependent on their founder for their continuing existence, as museums generally cannot cover expenses via revenues from ticket prices, museum shops and cafes:
The \textcite{IMLS_2008_funding} found that for non-profit American art museums, less than half (48.1\%) the revenues come from earned income, leaving substantial gaps in the budgets that are filled by a mix of private donations (23.0\%), investment (18.5\%) and government support (10.4\%) (p.27).
Outside of the United States, the reliance on revenue streams beyond operations is even larger:
German museums in the 1990s covered on average only around 30\% of their budget by their income \parencite{Martin_1993_museen}\footnote{Own calculations based on table p.233}, with private museums requiring less support as operations provide around 47\% of their budget (ibid.), and even the more market-oriented NPOs in the cultural sector draw around 50\% of their funding from public support \parencite[p.82]{Zimmer_Priller_2007_gemeinnuetzig}.
On a European level, only 12\% of museum incomes are generated by entry fees, whereas 69\% originate from subsidies \parencite{EGMUS_2024_complete.}\footnote{Own calculations from on EGMUS data, based on all countries with income data from 2015 onwards.}

@@

On a national level, density of private museum is calculated as the number of private museums per million population.
To measure competition on a local level, I first determine the coordinates of museum using the Google Maps API; the coordindates of museums which are not found that way (particularly those located in countries with limited Google presence such as South Korea, China and Russia) are searched manually (often using other map services such as Kakao Maps, Baidu Maps and Yandex Maps).
For closed museums, which often are not included in the current map databases, coordinates are also determined via addresses mentioned on snapshots in the Wayback Machine.
I then use the Global Human Settlement Layer \parencite{EC_2023_GHSL} to estimate the number of private museums and population counts inside a radius of ten kilometers around each private museum for each year.
To be able to estimate both competition and demand/audience/population separately, I do not calculate densities as per capita rates, but include the local museum counts, local population in millions as well as an interaction between the two.
\subsubsection*{Control variables}

@@

Previously the dozens of closures have been seen as indicator of their vulnerability and short-livedness \parencite{Adam_2020_close}, however this analysis shows the importance studying closing not in isolaton but in comparison to both non-closures and closures of comparable institutions.
While the booming numbers of private museums themselves have received substantial attention, less consideration has been given to the fact that large populations can generate dozens of closures without requiring high closing rates, especially when cloures are considered over a span of several years or decades.
In other words, the sheer size to which the private museum population has grown over the last decades has made it all but inevitable that some of them would close, and do so after only a few year.
Based on the current analysis, private museums will continue to close in the years to come; at hazard rates of around 1\% on average a handful of closures every year are to be expected.

Comparing private museums closures to closures of other organizational form advances our understanding of the sustainability of this new organizational form.
While private museums do close, the comparison to previous studies of museum closing rates provides no evidence that dependence on single founders constitutes a less stable organizational form than reliance on less centralized foundations, associations or corporate sponsorship.
Multiple reasons might be the at play that mitigate this risk of low diversification.
First, it might take more commitment to open a museum as an individual or couple compared to less involved art patronage of being a board member in existing institutions or donating works, which would result in private museums founders being more motivated to secure the existence of their institutions.
Furthermore, the centrality of the founder might leave little room to question who is responsible to provide additional funds in times of financial difficulties, whereas in organizations without a central figure each member may feel less responsible.
It might also be such commitment that leads founder to plan the future of their museum to such an extent that their death is not significantly associated with unvoluntary closing.

However, it is necessary to consider that so far only a small fraction (47 museums, 9.3\%) of museums has experienced the death of their founder, one of the primary reasons hypothesized to lead to the private museum closure. 
While so far these museums have not seen substantially elevated closing risks, these estimates will become more precise as more founders pass away.
As the currently large confidence interval (figure \ref{fig:p_surv_death}) for museums whose founders have died allows a wide range of survival chances, it is entirely possible that previous scholars have indeed correctly identified a key dependency (the current absence of evidence of it should not be taken as evidence of absence) and that therefore later analyses will a significantly association between founder death and closing risk as well as a higher average closing risk for private museums.
At the same time, it is also possible that private museums are generally less dependent on a single person (or couple) than has been assumed, and have in fact become institutionalized to an extent that most heirs of founders feel as motivated to continue the original founders' efforts as these founders themselves.

While so far little evidence points toward low diversification, i.e. reliance on the founder, as a key vulnerability of private museums to unvoluntary closures, the centrality of the founder may be more pronounced in voluntary closures. 
Indicated by unconventional naming choice, a subset of founders might from the very beginning envision the museum as temporary.
On the other hand, higher closing rates for unconventionally named museums might reflect absence of recognition and support by third parties in the environment.
While the question of which mechanism explains the association between name and survival, the role of the environment can be clearly seen in terms of nearby institution counts and population measures, with both factors leading to higher closing rates.

While overall private museum closing rates are generally not diverging from museums in general, and may even lie below the average, it has to be kept in mind that this comparison is based on American non-profit museums.
To the best of my knowledge, currently no data sources exist that allow estimation of closing rates of (European) public, state-funded museums.
While public museums have been characterized to some extent as very stable due to government picking up deficits \parencite{Meier_Frey_2003_faces,Bechtler_Imhof_2018_future}, \textcite{Walker_2019_collector} argues that due to declining cultural spending even public museums might face hard times.
Most national public flagship institutions will presumably remain sufficiently funded to survive, however this might not be the case for the much larger of smaller museums in less touristic regions who rely on more limited municipal funding (49\% of the European museum population, \cite{EGMUS_2024_complete}), as \textcite{StylianouLambert_etal_2014_museums} explore for a number of smaller publicly funded ethnography museums in Cyprus.
Yet without access to museum registers comparable to the IRS/NCCS datasets, questions regarding the relation between type of ownership and survival remain speculative.

\subsection*{Conclusion}

Private museum have been characterized as fragile institutions due to their reliance on a single founder.
However, my analysis finds neither a higher substantially higher mortality rates for private museums compared to (art) museums generally, nor a conclusive relationship between museum closure and a number of founder characteristics, such as founder gender, death, exclusion from the Artnews collector ranking or inclusion of founder name in the museum name.
While Self-identification and audience/competition are significantly associated with higher mortality, and possibly reflect or influence founder motivations, they are also subject to alternative mechanisms, namely devaluation by third parties and competition, respectively (self-identification furthermore concerns a relatively small group of institutions).
Furthermore, even if they reflect founder motivations, these are likely cases of voluntary closure; there is thus no large evidence that private museums are at a higher risk of unvoluntary closure than more diversified museums as a consequence of their reliance on a single founder. 
\subsubsection*{Limitations}

@@

egmus doesn't have that

\begin{sloppypar}
\printbibliography
\end{sloppypar}
\end{document}
